Ternary plots for `hyper2` and `hyper3` samples

### 2025-02-16 inst/ternaryplot_hyper2.Rmd
include ternary contour plot of chess

>>>>

```{r plotternarychess}
FunctionToContour <- function (a, b, c) {
    M <- cbind(a, b, c)
    colnames(M) <- c("Topalov", "Anand", "Karpov")
    M[] <- pmax(M,0)
    M <- sweep(M,1,rowSums(M),"/")
    out <- loglik(M, chess)
    out[is.infinite(out)] <- NA
    out <- out - max(out,na.rm = TRUE)
    out <- pmax(out, -20, na.rm = TRUE)
    return(out)
}

originalPar <- par(mar = rep(0, 4))
TernaryPlot(alab = "Topalov", blab = "Anand", clab = "Karpov")
values <- TernaryPointValues(FunctionToContour, resolution = 24L)
ColourTernary(
  values,
  legend = signif(seq(max(values), min(values), length.out = 4), 2),
  bty = "n"
)
TernaryContour(FunctionToContour, resolution = 72L, nlevels=10)
```
